---
title: "Machine Learning and Predictive Modelling 1"
author: "Leo, Lars, Niolas, Dominik"
date: "10/14/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install relevant packages

packages <- c("gitcreds",
              "tidyverse",
              "ggplot2",
              "readxl",
              "zoo",
              "car",
              "mgcv")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}

# Load relevant packages

library(gitcreds)
library(tidyverse)
library(ggplot2)
library(readxl)
library(zoo)
library(car)
library(mgcv)
library(e1071) 
library(caret)

#gitcreds_set() #Only needed in the first setup when git sync is not working with password only
```

## Data Perparation

```{r load, cache=TRUE}

# Load data

df <- read_excel("data/autos.xlsx")

# Create columns yearmon and age

df["yearmon"] = as.Date(as.yearmon(paste(df$yearOfRegistration,
                                         df$monthOfRegistration,
                                         sep = "-")))
df["age"] = as.numeric(as.Date(df$dateCreated) - df$yearmon)
```

## Data cleaning 1

The following filters were applied based on the investigations in the section "Investigate variables" The aim was to reduce the data set to less than 10^5 observations, to simplify it in terms of factor levels, to come up with reasonable ranges where enough data points were available and to get an approximative normal distribution for the variable values whenever possible.

```{r cleaning}

# Clean data step 1

df <- df %>% 
  filter(seller == "privat" &
           offerType == "Angebot" &
           price >= 500 &
           price <= 40000 &
           vehicleType != "andere" &
           !is.na(vehicleType) &
           !is.na(gearbox) &
           powerPS >= 50 &
           powerPS <= 325 &
           kilometer >= 10000 &
           kilometer <= 150000 &
           fuelType %in% c("benzin", "diesel") &
           !is.na(fuelType) &
           !is.na(notRepairedDamage) &
           !is.na(yearOfRegistration) & 
           !is.na(age) &
           age >= 180 &
           age <= 10000 &
           model != "andere" &
           lastSeen <= as.POSIXct("2016-04-04 23:59:59")) %>%
  select(-c("seller",
            "offerType",
            "abtest",
            "name",
            "nrOfPictures"))

# Keep brands with more than 1000 observations. Keep all models within the brands.

brand_table <- df %>%
  count(brand) %>%
  filter(n >= 1000)

brand_vector <- as.character(brand_table$brand)

model_table <- df %>%
  count(model) %>%
  filter(n >= 0)

model_vector <- as.character(model_table$model)

# Clean data step 2

df <- df %>% 
  filter(brand %in% brand_vector &
           model %in% model_vector)

# Change data types

str(df)
df <- df %>%
  mutate_if(sapply(df, is.character), as.factor) %>%
  mutate(kilometer = as.factor(kilometer))

```


## Investigate variables

As mentioned earlier, the following functions were used to get a better understanding of each variable and to filter them accordingly. The histogram provides information on the distribution of the data points within a variable. The quantile and ecdf function were used to try out different values and to spot anomalies and mistakes in the data set. They were also used to come up with the final ranges.
# TO DO: Is there a systematic process how to filter and decide ranges?

### Price

```{r investigatePriceVariable}

summary(df$price)
hist(df$price, xlab = "price", main = "Histogram response variable price")
quantile(df$price, 0.95)
ecdf(df$price)(17000)

```

Our response variable is extremely right-skewed as the histogram shows. Prices # range from 500 to 40'000. 95% of all observations show a price which is 17'000 or less. As our response variable is considered as amount, we will log-transform it in the modelling part. This helps also to reduce right-skewedness.

### Age

```{r investigateAgeVariable}

summary(df$age)
hist(df$age, xlab = "age in days", main = "Histogram age of cars")
quantile(df$age, 0.50)
ecdf(df$age)(4374)

```

Half of the cars offered are older than 4374 / 365 ~ 12 years. The data seems to approximately follow a normal distribution.

### powerPS

```{r investigatePowerPSVariable}

summary(df$powerPS)
hist(df$powerPS, xlab = "PS", main = "Histogram PS of cars")
quantile(df$powerPS, 0.75)
ecdf(df$powerPS)(120) - ecdf(df$powerPS)(100)

```

The distribution of the PS values is also right-skewed. About 20 % of all observations show values between 100 and 120 PS. Prices fitted from PS values should better fit in this range.

### kilometer

```{r investigateKilometerVariable}

summary(df$kilometer)
barplot(table(df$kilometer), xlab = "number of kilometers", main = "Mileage of cars")

```

The mileage variable form the data set is most likely a categorical variable where the advertiser could set a predefined value. The distribution is extremely left-skewed. The share of cars with 125'000 or more kilometers is around 75%.

### vehicleType

```{r investigateVehicleTypeVariable}

summary(df$vehicleType)
barplot(table(df$vehicleType))

```

Limousine, Kombi and Kleinwagen are the three dominant vehicle types.

### gearbox

```{r investigateGearboxVariable}

summary(df$gearbox)
barplot(table(df$gearbox))

```

The majority of cars advertised come with manual gearbox.

### brand & model

```{r investigateBrandAndModelVariable}

# summary(df$brand)
# nlevels(df$brand)
# summary(df$model)
# nlevels(df$model)

barplot(table(df$brand))

# ggplot(data=df, aes(x=brand, fill = model)) +
#   geom_bar(stat = "count") +
#   #scale_fill_brewer(palette = "Set3") + 
#   ggtitle("Brands and models") +
#   theme(axis.text.x = element_text(size = 12)) +
#   theme(axis.text.y = element_text(size = 12))

```

Volkswagen is the dominant car brand with more than 20'000 cars advertised. The VW Golf is the dominant model advertised, followed by the BMW 3er.

### fuelType

```{r investigateFuelTypeVariable}

summary(df$fuelType)
barplot(table(df$fuelType), main = "Fuel type of cars")
range(df$yearOfRegistration)

```

We focus on "Benzin" and "Diesel". There were no electric vehicles advertised in the data set which is not much of a surprise as the car registration values for the advertised cars range from 1988 to 2015.

### notRepairedDamage

```{r investigateNotRepairedDamageVariable}

summary(df$notRepairedDamage)
barplot(table(df$notRepairedDamage), main = "Repaired damage")

```

Around 10% of the advertised cars had a damage and were repaired before advertised.

## Graphical analysis

## Analysis of continuous variables:

```{r CreateTemplateContVariables}

template.scatterplot.df <- ggplot(data = df,
                                  mapping = aes(y = log(price))) +
  geom_point(alpha = 0.1) +
  geom_smooth()

```

### age

```{r AnalysisAge}

template.scatterplot.df + aes(x = age)

```

The relationship between age and price looks linear until an age of around 7000 days. Also the variance is pretty stable until then. Afterwards the variability increases significantly and the relationship changes from a negative effect to positive effect. Whether this can be modeled by a quadratic term will be checked later. There are some observations with a very low  price in the age range 5000 to 10000. We may need to check for that in the modelling part.

### powerPS

```{r AnalysisPowerPS}

template.scatterplot.df + aes(x = powerPS)

```

There is a clear positive effect of PS on price. whether the relationship is best modeled by a linear or higher order term needs to be evaluated. There is some bumpiness from around 220 PS on. Is this random noise due to decreasing observations or does that to be modeled?

### kilometer as continuous variable

```{r AnalysisKilometerCont}

template.scatterplot.df + aes(x = as.numeric(kilometer))

```

The mileage of the cars does have a negative effect on the price which is logical from a business point of view. It looks mostly like a linear relationship except for the low and high segments of the mileage. But be careful, the last two mileage levels show a distance of 25'000 kilometers in between. Not visible here are advertised cars with a mileage of 5000km. In the range of 5000 to 10000 kilometers the observations actually showed a positive on the price variable which is difficult to understand.

## Analysis of categorical variables

```{r CreateTemplateCatVariables}

template.boxplot.df <- ggplot(data = df,
                              mapping = aes(y = log(price))) +
  geom_boxplot()

```

### kilometer

```{r AnalysisKilometerCat}

template.boxplot.df + aes(x = kilometer)

```

There is a negative effect of kilometers on price. The effect is larger for the ladder levels. Also the variability increases for the ladder levels. The effects seem to be more or less normally distributed.

### vehicleType

```{r AnalysisVehicleType}

template.boxplot.df + aes(x = vehicleType)

```

There are some differences in prices for the different vehicle types. SUV's are the most # expensive cars whereas kleinwagen seem to be lowest in price. This is not a surprise. The variability for coupe is larger than for cabrio, kleinwagen, kombi, limousine and bus. The variability for suv semms to be the smallest with some outliers in the low price segment. If all the different vehicle types have a significant influence on price will be checked in the modelling part.

### gearbox

```{r AnalysisGearbox}

template.boxplot.df + aes(x = gearbox)

```

It seems to be that automatic gearbox are advertised with higher prices. From a business perspective, this makes perfect sense.

### fuelType

```{r AnalysisFuelType}

template.boxplot.df + aes(x = fuelType)

```

Cars with fuel type Diesel are advertised with higher prices. This is also in line with our business understanding.

### notRepairedDamage

```{r AnalysisNotRepairedDamage}

template.boxplot.df + aes(x = notRepairedDamage)

```

Cars with a previous damage are advertised with lower prices. Also common sense. Whether the effect is significant will be checked in the modelling part.

### brand

```{r AnalysisBrand}

template.boxplot.df + aes(x = brand)

```

Cars form the brand mini show the highest median price whereas Renault cars show the lowest. The brands do show different variability in price.

### model

```{r AnalysisModel}

template.boxplot.df + aes(x = model)

```

There are considerable differences between the different models. We will check the boxplots for the brand again but this time we distinguish between the models.

## Further considerations
Do we have other variables to control for where an effect is different among the levels of another factor? Or in other words, is there any interaction between the predictor variables?
- For example is the kilometer depreciation in price different among the brands?
- Is the age depreciation in price different among the brands?
- Or is the depreciation in price from kilometers and age different among the vehicle types?
We will focus for now on the graphical analysis and test these hypotheses later in the modelling part.

### Age versus brand

```{r AnalysisAgeVersusBrand, cache = TRUE}

ggplot(data = df,
       mapping = aes(y = log(price), x = age)) +
  geom_point(alpha = 0.1) +
  geom_smooth() +
  facet_wrap(. ~ brand)

```

We can see that the price depreciation from age behaves similarly among the different brands. From a certain age on the we can observe a positive effect on price. For some brands we do do not have many data points for older vehicles.

### Kilometer versus brand

```{r AnalysisKilometerVersusBrand, cache = TRUE}

ggplot(data = df,
       mapping = aes(y = log(price), x = as.numeric(kilometer))) +
  geom_point(alpha = 0.1) +
  geom_smooth() +
  facet_wrap(. ~ brand)

```

We changed the kilometer variable to numeric in order to plot a smoother to compare the different brands. Again, the behavior looks similar. BMW cars tend to have higher depreciation in the beginning and the end. For kilometers between 20 and 40k BMW's tend to raise in value. This is really interesting. The same behavior can be observed for the brands Mercedes-Benz and Opel, which have periods where the effect of depreciation is not linearly negative until about 50'000 km driven. There are brands were we do not have many data points for a short mileage.

### Age versus VehicleType

```{r AnalysisAgeVersusVehicleType, cache = TRUE}

ggplot(data = df,
       mapping = aes(y = log(price), x = age)) +
  geom_point(alpha = 0.1) +
  geom_smooth() +
  facet_wrap(. ~ vehicleType)

```

Again the curves look similar in terms of age depreciation among the different vehicle types. There is a change of the effect on price from negative to positive from a certain age on. For the vehicle type suv's there are not many observations for an age older than 5000 days.This could indicate that SUV's became popular only recently. For cabrios the turning point is around 7000 days. From there on, cabrios gain in value faster than other vehicle types. This may be due to the attraction of vintage cabrios.

### Kilometer versus VehicleType

```{r AnalysisKilometerVersusVehicleType, cache = TRUE}

ggplot(data = df,
       mapping = aes(y = log(price), x = as.numeric(kilometer))) +
  geom_point(alpha = 0.1) +
  geom_smooth() +
  facet_wrap(. ~ vehicleType)

```

The graphics look similar except for coupes and kombis. Coupes are gaining in value until about 50'000 kilometers driven. This seems counter-intuitive and may be due to the fact that there are not many data points until then.

## Fitting a linear model

We start by including all predictors without any interactions:

```{r lm.autos_1, results = "hide", cache = TRUE}

lm.autos_1 <- lm(log(price) ~ age + powerPS + kilometer + gearbox + brand + model + fuelType +
                   notRepairedDamage + vehicleType,
                 data = df)
summary(lm.autos_1)

```

The model seems to be quite good with 86% of the variability explained. However, there are 4 coefficients with an NA value. After googling, that tells us some of our variables are perfectly dependent on one or more other variables. We can check that with the alias function.

```{r aliasLm.autos_1, results = "hide"}

alias(lm.autos_1)

```

Let's take the example of the model Citroen c5. Indeed, it makes sense that whenever the brand is Citroen and the model is not berlingo, c1, c2, c3 or c4 it must be a c5. So including the brand and the model as two separate variables makes no sense as the brand is already defined through the model. We can simply solve that issue by only including the model type.

```{r lm.autos_2, results = "hide", cache = TRUE}

lm.autos_2 <- lm(log(price) ~ age + powerPS + kilometer + gearbox + model + fuelType +
                   notRepairedDamage + vehicleType,
                 data = df)
summary(lm.autos_2)

```

If we compare the summary statistics of lm.autos_1 with lm.autos_2 we state that the model got simpler as there are less variables but the variability explained remains unchanged. We now check our model for collinearity.

```{r collCheckLm.autos_2}

vif(lm.autos_2)

```

We can see that the GVIF value for the variable "model" is way too large. This indicates that the model variable is correlated to a linear combination of other variables. In our case, that could mean that the "model" is highly correlated with other variables just as powerPS, gearbox, vehicleType and so on. We therefore exclude the "model" variable and replace it with "brand".

```{r lm.autos_3, results = "hide", cache = TRUE}

lm.autos_3 <- lm(log(price) ~ age + powerPS + kilometer + gearbox + brand + fuelType +
                   notRepairedDamage + vehicleType,
                 data = df)
summary(lm.autos_3)

```

Our model does now have fewer parameters to fit and therefore became simpler. We lost some of the explained variability which is logical as we have less parameters. We check again for collinearity.

```{r collCheckLm.autos_3}

vif(lm.autos_3)

```

Now there seems to no problem anymore. From here on We test if all predictors do have a significant effect on the response variable with the drop1 command:

```{r drop1Lm.autos_3, cache = TRUE}

drop1(lm.autos_3, test = "F")

```

We can clearly state that all predictors do have a strong effect on the response variable. We now include the relevant two-fold interactions as figured out in the graphical analysis.

```{r lm.autos_4, results = "hide", cache = TRUE}

lm.autos_4 <- lm(log(price) ~ age + powerPS + kilometer + gearbox + brand + fuelType + 
                   notRepairedDamage + vehicleType + age:brand + age:vehicleType +
                   kilometer:brand + kilometer:vehicleType, data = df)
summary(lm.autos_4)
alias(lm.autos_4)

```

Including the relevant two-fold-interactions, the variability explained increases slightly. Again we check if all predictors including the two-fold-interactions have a significant effect on the response variable.

```{r drop1Lm.autos_4, cache = TRUE}

drop1(lm.autos_4, test = "F")

```

All of our predictors and interactions do have a strong effect on our response variable. The variability explained is around 85%.

We now check if we need to model non-linear effects. As previously seen in the graphical analysis. The assumption is that the age variable has a quadratic effect on the response variable. Therefore we try to model that with a poly function.

```{r lm.autos_5, results = "hide", cache = TRUE}

lm.autos_5 <- lm(log(price) ~ (poly(age, degree = 2) + powerPS + kilometer + gearbox + brand + fuelType +
                                 notRepairedDamage + vehicleType + poly(age, degree = 2):brand + 
                                 poly(age, degree = 2):vehicleType + kilometer:brand + kilometer:vehicleType),
                 data = df)

anova(lm.autos_4, lm.autos_5)
summary(lm.autos_5)
drop1(lm.autos_5, test = "F")

```

There is strong evidence that age needs a quadratic term. So we leave that.

We now have our final linear model with explained variability of around 85%. All predictors do have a strong effect on the response variable. The variables brand and vehicle type have a mixed effect. The coefficients for the parameters powerPS, fuelTypediesel and notRepairedDamagenein are positive and therefore have a positive effect on the response variable price. The coefficient for the parameter gearboxmanuell is negative and therefore has a negative impact on price. Interestingly, the kilometer and age parameters show a different influence on price. Whereas for up to 90'000 kilometers they have a mixed influence, the effect from 100'000 kilometers on is clearly negative. This is a bit counter-intuitive and it would be interesting to check that with business people. An interpretation of all interaction terms is omitted.

## Predicted values

### Calculating in-sample RMSE

```{r calRMSEInSampleLm, cache = TRUE}

pred.lm.autos_5.in_sample <- predict(lm.autos_5, df)
error <- exp(pred.lm.autos_5.in_sample) - df$price
sqrt(mean(error^2))

```

Our model is off by 2390 Euros for each car. This seems not to be satisfactory result.

### Calculating in-sample MAPE

```{r calMAPEInSampleLm}

residuals <- exp(pred.lm.autos_5.in_sample) - df$price
ape <- abs(residuals) / df$price
mean(ape)

```

This means that our price prediction deviates on average 30% from the actual price.

We want a model that does not overfit an generalize well. To answer the question if our model performs well on new data, we split up our data set randomly into a test and training data set, apply our model on the training data set and test it with the test data set.

```{r CreateTrainingandTest, cache = TRUE}

set.seed(42)
rows <- sample(nrow(df))
df.sample <- df[rows, ]

split <- round(nrow(df) * 0.80)
df.train <- df.sample[1:split, ]
df.test <- df.sample[(split + 1):nrow(df.sample), ]

lm.autos_5_sample <- lm(log(price) ~ (poly(age, degree = 2) + powerPS + kilometer + gearbox + brand + fuelType +
                                 notRepairedDamage + vehicleType + poly(age, degree = 2):brand + 
                                 poly(age, degree = 2):vehicleType + kilometer:brand + kilometer:vehicleType),
                        data = df.train)

```

### Calculating out-of-sample RMSE

```{r calRMSEOutSampleLm, cache = TRUE}

pred.lm.autos_5.out_sample <- predict(lm.autos_5_sample, df.test)
error <- exp(pred.lm.autos_5.out_sample) - df.test$price
sqrt(mean(error^2))

```

### Calculating out-of-sample MAPE

```{r calMAPEOutSampleLm}

residuals <- exp(pred.lm.autos_5.out_sample) - df.test$price
ape <- abs(residuals) / df.test$price
mean(ape)

```

There are no major deviations from the in-sample testing, so at least our model generalizes well. We leave it like that for the moment and hope for better results with different models.

# TODO: Cross-validation and residual analysis.

## Fitting a gam model

In our data set we do have age and powerPS, two continuous variables with a possible non-linear effect. We allow them have a non-linear effect by specifying the smooth terms s(age) and s(powerPS) in the model. As a basis we use our linear model from above without any interactions.

```{r gam.autos_1, results = "hide", cache = TRUE}

gam.autos_1 <- gam(log(price) ~ s(age) + s(powerPS) + kilometer + gearbox + brand + fuelType +
                                 notRepairedDamage + vehicleType,
                 data = df)
summary(gam.autos_1)

```

The summary output indicates that there there is strong evidence that age and powerPS have a non-linear effect on the response variable. The estimated degrees of freedom quantify the complexity of the smooth functions. Let’s visualise the effects of the variable age and powerPS.

```{r plotGam, cache = TRUE}

plot(gam.autos_1, residuals = TRUE, select = 1, col = alpha("black", 0.1), shade = TRUE)
plot(gam.autos_1, residuals = TRUE, select = 2, col = alpha("black", 0.1), shade = TRUE)

```

From a visual perspective, it is hard to interpret the estimated degrees of freedom for the smooth terms age and powerPS.

Let's now fit our gam model with the interactions from the previously defined linear model.

```{r gam.autos_2, results = "hide", cache = TRUE}

gam.autos_2 <- gam(log(price) ~ s(age) + s(powerPS) + kilometer + gearbox + brand + fuelType +
                     notRepairedDamage + vehicleType + s(age, by = brand) + s(age, by = vehicleType) +
                     kilometer:brand + kilometer:vehicleType,
                   data = df)
summary(gam.autos_2)
anova(gam.autos_1, gam.autos_2, test = "F")

```

There is strong evidence that the model with the interactions better explains the effect on the response variable. We will trust our gam model by now and make some predictions in the same way we already did for the linear model.

## Predicted values

### Calculating in-sample RMSE

```{r calRMSEInSampleGam, cache = TRUE}

pred.gam.autos_2.in_sample <- predict(gam.autos_2, df)
error <- exp(pred.gam.autos_2.in_sample) - df$price
sqrt(mean(error^2))

```

Our model is off by 2130 Euros for each car. This is slightly better than with the linear model.

### Calculating in-sample MAPE

```{r calMAPEInSampleGam}

residuals <- exp(pred.gam.autos_2.in_sample) - df$price
ape <- abs(residuals) / df$price
mean(ape)

```

This means that our price prediction deviates on average 28% from the actual price.

### Calculating out-of-sample RMSE

```{r calRMSEOutSampleGam, cache = TRUE}

gam.autos_2_sample <- gam(log(price) ~ s(age) + s(powerPS) + kilometer + gearbox + brand + fuelType +
                     notRepairedDamage + vehicleType + s(age, by = brand) + s(age, by = vehicleType) +
                     kilometer:brand + kilometer:vehicleType,
                     data = df.train)

pred.gam.autos_2.out_sample <- predict(gam.autos_2_sample, df.test)
error <- exp(pred.gam.autos_2.out_sample) - df.test$price
sqrt(mean(error^2))

```

### Calculating out-of-sample MAPE

```{r calMAPEOutSampleGam, cache = TRUE}

residuals <- exp(pred.gam.autos_2.out_sample) - df.test$price
ape <- abs(residuals) / df.test$price
mean(ape)

```

There are no major deviations from the in-sample testing, so the model generalizes well. Also for the gam model the results are not convincing. This may lead to the conclusion that linear models and their extensions are not very well suited to predict prices for the given data set.

# TODO: Cross-validation and residual analysis.


## Support Vector Machines

In this part we use support vector machines models for classification. Because the main application area for svm are classification tasks we decided to create a new variable called "priceGroup" which splits the continuse variable price into 4 groups. to find a suitable range for the groups we boxplot the price again and have a look at the 25% / 50% and 75% quartile.

```{r}
#Adding price groups for classifaction purpose
quantile(df$price)
```


```{r}
#Adding price groups for classifaction purpose
df_svm <- df
df_svm$priceGroup <- as.factor(sapply(df$price, function(x)
  if (x < 1550)   'cheap'
  else if (x <=3400)  'economy'
  else if (x <=7000) 'upscale'
  else 'premium'
))
df_svm$kilometer <- as.numeric(df_svm$kilometer)
```

We can see that cars with not repaired Damages are cheaper in every brand which makes sense from a business point of view.

## Model 1 - Use all possible predictors for SVM (linear)

```{r}
set.seed(193)
df_svm_1_full<-df_svm[c("priceGroup","vehicleType","gearbox","powerPS","model","kilometer","fuelType","brand","notRepairedDamage","postalCode","age")]
df_svm_1_sample<-df_svm_1_full[sample(nrow(df), 20000), ]
```

## Prepare the Data for Training

```{r}
set.seed(193)
indices <- createDataPartition(df_svm_1_sample$priceGroup, p=.85, list = F)
```

### Create some easy Variables to access Data

```{r}
train <- df_svm_1_sample %>%
  slice(indices)
test_in <- df_svm_1_sample %>%
  slice(-indices) %>%
  select(-priceGroup)
test_truth <- df_svm_1_sample %>%
  slice(-indices) %>%
  pull(priceGroup)
```


## Train the SVM

Call the `svm` function using the default `cost = 10` parameter.

```{r}
set.seed(123)
cars_svm <- svm(priceGroup ~ ., train, kernel = "linear", scale = TRUE, cost = 10)
```

Of course the visualization is a bit difficult as we have some classification regions in four dimensions.

So plot first the resulting classification for the two Petal leaf dimensions

```{r}
plot(cars_svm, train, kilometer ~ age)
```

## Make Predictions

```{r}
test_pred <- predict(cars_svm , test_in)
table(test_pred)
```
## Evaluate the Results

```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```

## Model 2 - Use all possible predictors for SVM (radial)


```{r}
set.seed(123)
cars_svm2 <- svm(priceGroup ~ ., train, kernel = "radial", scale = TRUE, cost = 10)
summary(cars_svm2)
```

```{r}
plot(cars_svm2, train, kilometer ~ age)
```


```{r}
test_pred <- predict(cars_svm2, test_in)
table(test_pred)
```
```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```


## Model 3 - Use only use model (linear)


```{r}
set.seed(123)
cars_svm2 <- svm(priceGroup ~ model, train, kernel = "linear", scale = TRUE, cost = 10)
summary(cars_svm2)
```


```{r}
test_pred <- predict(cars_svm2, test_in)
table(test_pred)
```
```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```

## Model 4 - Use only use model (radial)


```{r}
set.seed(123)
cars_svm2 <- svm(priceGroup ~ model, train, kernel = "radial", scale = TRUE, cost = 10)
summary(cars_svm2)
```


```{r}
test_pred <- predict(cars_svm2, test_in)
table(test_pred)
```
```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```

## Model 5 - Use only use kilometer and age (linear)


```{r}
set.seed(123)
cars_svm2 <- svm(priceGroup ~ age + kilometer, train, kernel = "linear", scale = TRUE, cost = 10)
summary(cars_svm2)
```


```{r}
test_pred <- predict(cars_svm2, test_in)
table(test_pred)
```
```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```


## Model 6 - Use only use kilometer and age (radial)


```{r}
set.seed(123)
cars_svm2 <- svm(priceGroup ~ age + kilometer, train, kernel = "radial", scale = TRUE, cost = 10)
summary(cars_svm2)
```


```{r}
test_pred <- predict(cars_svm2, test_in)
table(test_pred)
```
```{r}
conf_matrix <- confusionMatrix(test_pred, test_truth)
conf_matrix
```